---
title: "Mango"
author: "Christopher Hughes"
date: "17 February 2017"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Mango Solutions - R Coding Test"
author: "Christopher Hughes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

R Coding Test
============

1. Create a vector of length 26, containing samples from a normal distribution

```{r}
norm_26 <- rnorm(26)
```

2. Print the minimum, maximum, median, 25% and 75% quantiles of this data.

```{r}
# Exclude the mean - fourth element in the vector
summary(norm_26)[-4]
```

3. Create a 10x10 matrix of samples from a Poisson distribution (lambda=1).

```{r}
n <- 100
d <- 10
pois_100 <- matrix(rpois(n, 1), d)
```

4. Print the maximum of each row of the matrix.

```{r}
# max columns randomly gives the index when there is a tie
max_i <- max.col(pois_100)
# index the original values with max_i nice to have the index
pois_100[cbind(seq(10),max_i)]

# Or use apply - tidier solution
apply(X = pois_100, MARGIN = 1, FUN = max)

# Use apply with an anonymous function - flexible
row_max <- apply(X = pois_100, MARGIN = 1, FUN = function(x){max(x)})
```

5. Store the created vector and matrix in a “list” structure

```{r}
list_r <- list(pois_100, row_max)
```

6. Print the length of each component of the list.

```{r}
lapply(list_r,FUN = length)

```

7. Create a function to output the maximum of each row of a matrix. Then use this function to re-run the question 4.

```{r}
row_max <- function(x){
  apply(X = x, MARGIN = 1, FUN = function(x){max(x)})
}
row_max(pois_100)
```

Extension
===============

1. Write a function that will simulate numbers from a given distribution. The function should take one argument for the number of samples and a second argument which specifies the distribution (Normal, Poisson or Binomial). The function should be able to handle additional parameters depending on the distribution chosen, e.g. a ‘lambda’ for Poisson samples.

```{r}
sim_values <- function(n, dist = "Normal", ...) {
  
  if (tolower(dist) == "normal") {
    mean <- list(...)$mean
    sd <- list(...)$sd
    if (is.null(mean)) {
      mean <- 0
    }
    if (is.null(sd)) {
      sd <- 1
    }
    rnorm(n, mean, sd)
  }
  
  else if (tolower(dist) == "poisson"){
    lambda <- list(...)$lambda
    if (is.null(lambda)) {
      lambda <- 1
    }
    rpois(n, lambda)
  }
  
  else if (tolower(dist) == "binomial") {
    size <- list(...)$size
    prob <- list(...)$prob
    if (is.null(size)) {
      size <- 10
    }
    if (is.null(prob)) {
      prob <- 0.5
    }
    rbinom(n, size, prob)
  }
  
}
```

We can see the function in action:

```{r}
library(ggplot2)
df_sim <- data.frame(Values =sim_values(1000, dist = "NORMAL", mean = 5))

ggplot() + geom_histogram(data = df_sim,mapping = aes(Values), bins = 30,
                          fill = "red", alpha = 0.5)
```
